### 2019-07-12 papers/journal/intro.tex
asd

%\subsection{Synthesis of VTS:}
%
The underlying cell biology dictates the set of basic constraints the VTS should follow.
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We use our graph connectivity results as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%

%\subsection{Analysis is difficult problem}
The analysis of VTSs is a difficult problem because
of the combinatorial scaling of possible traffic topologies and
regulatory rules.
%
Analysis on a large number of graphs~\footnote{There are total 68715 simple (no parallel edges) 3-connected graphs with 8 nodes} jointly with combinatorially many possible regulatory rules (all compatible labels of edges and nodes etc.) will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

In previous work, a sampling approach was undertaken. 
%
The study used a rule-based approach~\cite{mani2016stacking}, where given an initial condition of the cell, and rules for molecular traffic, the state of each compartment in the cell is updated until a steady state is reached. 
%
With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
%
Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
%
It is possible that a different scheme for the dynamics could lead to a different set of solutions.

@@

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT,  SMT, and QBF solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
%
In a recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle the system with just 8 compartments).
%
Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled using sampling and left open.
%
In this paper, we present both the SMT and QBF encodings to address these two problems.
%
%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
%\subsection{Previous work and our Contribution}
%
%The following are the contributions of this work:
%\begin{itemize}
%	\item We have added novel encoding reachability and 3-4 connectivity
%	\item Direct encoding into the SAT solver
%	\item A user friendly and scalable tool based on well known SMT solver Z3
%\end{itemize}

\par We have implemented the encodings in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
%
We have applied our synthesis tool on several VTSs including
two found-in-nature VTSs.
%
We manage to scale the tool to the size that makes the tool biologically relevant. 
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

%
The rest of the paper is organized as follows. 
%
In Section~\ref{sec:bio}, we present the biological background and details to understand the VTS. 
%
In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
%
In Section~\ref{sec:model}, we present a formal model of VTSs and in section~\ref{sec:problem}, we present the property of interest with their formal problem statements of different search problems of VTS.
%
In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
%
In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
%
In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~

>>>>

%\subsection{Synthesis of VTS:}
%
The underlying cell biology dictates the set of basic constraints the VTS should follow.
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We use our graph connectivity results as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties, which we can then test experimentally.
%

%\subsection{Analysis is difficult problem}
The analysis of VTSs is a difficult problem because
of the combinatorial scaling of possible traffic topologies and
regulatory rules.
%
An analysis of a large number of graphs~\footnote{There are total 68715 simple (no parallel edges) 3-connected graphs with 8 nodes} jointly with combinatorially many possible regulatory rules (all compatible labels of edges and nodes etc.) will be difficult to handle by any tool.
%
The same reason would hinder the precise analysis of the properties of the VTS.

A previous work used a sampling approach. 
%
The study used a rule-based approach~\cite{mani2016stacking}.
Given an initial condition of the cell and rules for molecular traffic,
the approach updates the state of each compartment in the cell until the cell reaches a steady-state. 
%
With this study, statistical claims can be made, but improbable albeit biologically possible solutions could have been missed.
%
Also, there are many ways in which the dynamics of vesicle transport can be played out, while a single one was explored in this work. 
%
It is possible that a different scheme for the dynamics could lead to a different set of solutions.

@@

In contrast, here we seek to understand the properties of vesicle traffic networks
over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT (Boolean satisfiability), SMT (satisfiability modulo theories) and QBF (quantified Boolean formula) solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can predict the hypothesis for all possible states of the system without explicit enumeration of rules. 
%
In recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient. The tool was able to handle the system with just eight compartments.
%
Another interesting question of property involving quantifiers (was termed as sufficient condition i
n \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
using sampling and left open.
%
In this paper, we present both the SMT and QBF encodings to address the two problems.
%

%
%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
%\subsection{Previous work and our Contribution}
%
%The following are the contributions of this work:
%\begin{itemize}
%	\item We have added novel encoding reachability and 3-4 connectivity
%	\item Direct encoding into the SAT solver
%	\item A user friendly and scalable tool based on well known SMT solver Z3
%\end{itemize}

\par We have implemented the encodings in a flexible tool, which can handle both connectivity questions and a wide range of synthesis queries. 
%
We have applied our synthesis tool on several VTSs, including
two found-in-nature VTSs.
%
We manage to scale the tool to the size that makes the tool biologically relevant. 
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

%
We organized the rest of the paper as follows. 
%
In Section~\ref{sec:bio}, we present the biological background and details to understand the VTS. 
%
In Section~\ref{sec:prelim}, we present the notations we use in this paper. 
%
In Section~\ref{sec:model}, we present a formal model of VTSs, and in section~\ref{sec:problem}, we present the property of interest with their formal problem statements of different search problems of VTS.
%
In Section~\ref{sec:encoding}, we present the encodings of corresponding search problems. 
%
In Section~\ref{sec:experiments}, we present our implementation and experimental results. 
%
In Section~\ref{sec:related}, we discuss related work and conclude in Section~\ref{sec:conclusion}.
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~
